---
title: "dative_list_generation"
author: "Steve Schwering"
date: "1/12/2021"
output: html_document
---

```{r}
sentences = read_csv('generated_pairs_with_results.csv')
verbs = read_csv('verblists.csv')
```

Let's identify the most DO-biased and most PO-biased verbs

```{r}
verb_do_biases = sentences %>%
  group_by(verb_id) %>%
  summarise(m_do_pref = mean(BehavDOpreference),
            se_do_pref = se(BehavDOpreference)) %>%
  left_join(verbs, by = 'verb_id')
```

Identify the most DO-biased sentence for each verb. Filter to exclude sentences with a `something` theme and with a `pronoun` recipient_id.

```{r}
verb_most_biased = sentences %>%
  filter(theme_type != 'something' & recipient_id != 'pronoun') %>%
  group_by(verb_id) %>%
  top_n(1, BehavDOpreference) %>%
  left_join(verb_do_biases, by = 'verb_id')
```

Most of these appear to use the same indirect object (e.g. `the man`, `the woman`). It would probably be good to identify our own indirect objects, but that set is much less constrained than direct objects.

Anyway, now we can extract only the content words. To do this, I am going to identify the set of words that we do NOT want and simply remove them, and then convert the string to a list.

```{r}
superfluous = c("the", "a")

sentences = sentences %>%
  mutate(stripped_sentence = str_split(DOsentence, ' '),
         stripped_sentence = map(stripped_sentence, purrr::discard(., .p = ~stringr::str_detect(.x, superfluous))))
```
